\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-02 paper.tex
added code of +++ parser
modified alternation section

    Applying this parser to an input string ``12rera" will succeed with the result [((`1', `2'), ``rera")] whereas in case of an input ``1rera" will fail and return [ ] since the second parsed character \textit{`r'} is not a digit. \\ \\
    Nevertheless, it would not be convenient to create new parsers each time more items need to be parsed. For that reason, \textit{recursive parsers} are desired. Additionally, recursive operation must be terminated at some point. In order to achieve or not termination, the \textbf{alternation} combinator has to be used but more on that on the next subsection.

    \subsubsection{Alternation}

>>>>

    Applying this parser to an input string ``12rera" will succeed with the result [((`1', `2'), ``rera")] whereas in case of an input ``1rera" will fail and return [ ] since the second parsed character \textit{`r'} is not a digit. \\ \\
    Nevertheless, it would not be convenient to create new parsers each time more items need to be parsed. For that reason, \textit{recursive parsers} are desired. Additionally, recursive operation must be terminated at some point. In order to achieve or not termination, the \textbf{alternation} combinator has to be used but more on that on the next subsection.
    \subsubsection{Alternation}

    In this subsection, the attention will be redirected towards producing alternation in parsers.  The implementation of 2 parsers being alternated together will be represented by the operator (\texttt{+++}) and we will refer to this as the \textbf{plus} parser. Have a look at the following Haskell snippet to understand how alternation is attained:

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell]
      (+++) :: Parse a -> Parse a -> Parse a
      p +++ q  = \input -> (p input ++ q input)
    \end{lstlisting}
    \end{tcolorbox}

    \noindent At the moment, even though the first parser will succeed in parsing the input, the second parser will always be applied to the same input. This is not the desired behaviour from alternation of parsers. The goal is to allow the second parser to parse the input string only if the initial parser has failed in doing so. Additionally, if the first parser succeeds in parsing the input, the program is terminated and the parsed result is returned. This approach will introduce a deterministic behavior in the alternation of parsers. How can this be achieved? In order to achieve this attitude between the initial parser and the latter parser, the primitive \textit{zero} parser will be exploited. Recalling from section 5.2, the \textit{zero} parser will take any input and return absolutely nothing.

    \subsection{Conclusions}
